A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-11 MSRChallenge2016.tex
changes
changes for Hoan

\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} ask
some of the same questions we do, on  5 projects. We study a much
larger dataset~\cite{dyer2013} with 380,125 repositories; and we look at more
statement types, as well as replacements. Similar to our study in
Section~\ref{sec:stmtstudy}, researchers have 
studied AST-level~\cite{Martinez:2015ez} and line-level
changes~\cite{Asaduzzaman:2013df} across bug fixing commits.
Although the granularity differs, our approach is also novel with respect to scale of
analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
understand the ``Plastic Surgery Hypothesis'' underlying certain types of
program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
analyze changes to Java programs to inform automated repair, and
show that doing so results in higher-quality repairs; we study their templates
heuristically on a different dataset. Their results motivate studies of human
repairs, as it may result in better patches.  Long and Rinard learn
probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
significantly less precise and does not inform a new technique.  Rather, it
serves as a starting point for research on the repair of Java bugs.

@@

\vspace{1ex}
\noindent\textbf{How often do developers introduce new classes, methods, fields,
	local variables in
bug fixing commits?} 
%
This question is interesting because most automatic program repair approaches
do not create methods or variable declarations, nor do most explicitly consider
object-oriented features, like fields or classes. 
%
Table~\ref{tbl:new} shows that introducing new
classes or variables is rare. On average, we still have $0.69$ new methods
per bug fix. These methods include new test methods (annotated by
@Test, for example), which is not too alarming. However, we note
that $1.32$ fields are created per bug fix, suggesting
that automatic program repair approaches should pay attention to the state of
the class when fixing Java programs.

@@

\noindent\textbf{Lessons learned.} The findings of our study provide useful
insights for automatic program repair tools in Java. It suggests that patterns
proposed by the state-of-the-art approaches for Java are insufficient to cover
the extent of bug fixes in our dataset.  Adding more patterns is one solution,
but may not be a general one.  Our findings further suggest that mutation based
program repair may need to consider field or method insertion to achieve
human-comparability in patches. This finding indicates that direct translation
of mutation based approaches from C to Java is not likely to succeed due to the
different language constructs.  A deeper look suggests that such techniques may
benefit from leveraging probabilistic knowledge of what types of statements are
commonly inserted, deleted, or replaced in Java bug-fixing commits. Again, the
probabilistic knowledge for C is not likely to work for Java program if
different coding conventions are considered.  Overall, our findings motivate
additional study of repair in Java, as assumptions that underlie approaches that
target C seem unlikely to translate directly.

>>>>

\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} ask
some of the same questions we do, on 6 projects. We study a much
larger dataset~\cite{dyer2013} with 380,125 repositories; and we look at more
statement types, as well as replacements. Similar to our study in
Section~\ref{sec:stmtstudy}, researchers have 
studied AST-level~\cite{Martinez:2015ez} and line-level
changes~\cite{Asaduzzaman:2013df} across bug fixing commits.
Although the granularity differs, our approach is also novel with respect to scale of
analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
understand the ``Plastic Surgery Hypothesis'' underlying certain types of
program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
analyze changes to Java programs to inform automated repair, and
show that doing so results in higher-quality repairs; we study their templates
heuristically on a different dataset. Their results motivate studies of human
repairs, as it may result in better patches.  Long and Rinard learn
probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
significantly less precise and does not inform a new technique.  Rather, it
serves as a starting point for research on the repair of Java bugs.

@@

\vspace{1ex}
\noindent\textbf{How often do developers introduce new classes, methods, fields,
	local variables in
bug fixing commits?} 
%
This question is interesting because most automatic program repair approaches
do not create methods or variable declarations, nor do most explicitly consider
object-oriented features, like fields or classes. 
%
The bottom section of Table~\ref{tbl:new} shows that introducing new
classes or variables is rare. On average, we still have $0.69$ new methods
per bug fix. These methods include new test methods (annotated by
@Test, for example), which is not too alarming. However, we note
that $1.32$ fields are created per bug fix, suggesting
that automatic program repair approaches should pay attention to the state of
the class when fixing Java programs.

@@

\noindent\textbf{Lessons learned.} The findings of our study provide useful
insights for automatic program repair tools in Java. It suggests that patterns
proposed by the state-of-the-art approaches for Java are insufficient to cover
the extent of bug fixes in our dataset.  Adding more patterns is one solution,
but may not be a general one.  Our findings further suggest that mutation based
program repair may need to consider field or method insertion to achieve
human-comparability in patches. This finding indicates that direct translation
of mutation based approaches from C to Java is not likely to succeed due to the
different language constructs.  A deeper look suggests that such techniques may
benefit from leveraging probabilistic knowledge of what types of statements are
commonly inserted, deleted, or replaced in Java bug-fixing commits. Again, the
probabilistic knowledge for C is not likely to work for Java program if
different coding conventions are considered.  Overall, our findings motivate
additional study of repair in Java, as assumptions that underlie approaches that
target C are unlikely to translate directly.
